Turbulence in compact to giant H~II regions

### 2022-12-14 strucfunc_paper.tex
Javier changes 2022-12-13

%methods for our analysis
We look for correlations and scaling relations 
between the physical parameters of the \hii{} regions
and the parameters of the fluctuating velocity fields
that we derived in section~\ref{sec:results}.
To accomplish this we implement a hierarchical Bayesian model for linear regression using the \texttt{linmix} Python library, which is based on the procedure of \cite{2007ApJ...665.1489K}.
We fit relations of the form
\(Y = a X + b\)
where \(X = \log_{10} x\) and \(Y = \log_{10} y\)
with \(x, y \in \{d, D, L(\ha), \sigma\pos, r_0, m\}\)
(taken from the physical properties in Table~\ref{tab:regions-properties}
and the derived turbulent parameters of Table~\ref{tab:Res}).
Thus the fitted relation between the original variables
is of the power-law form: \(y = 10^b\, x^a\).
Note that, unlike with an Ordinary Least Squares method,
the \citeauthor{2007ApJ...665.1489K} method
uses an errors-in-variables model that allows for
measurement uncertainty in both \(X\) and \(Y\).
Since the main focus of this paper is the turbulent velocity field,
we restrict consideration to correlations that include
one of the three structure function parameters,
\(\sigma\pos\), \(r_0\), or \(m\), as the  \(y\) variable. 
In addition, we fit a strictly linear relationship between
the plane-of-sky and line-of-sight velocity dispersions:
\(X = \sigma\pos\), \(Y = \sigma\los\).
The reason for not taking the logarithm in this instance is
both to facilitate comparison with previous studies
and to allow for a zero-point offset in the relation.

@@

\subsubsection{The constancy of the power law slope}
\label{sec:constancy-power-law}
The slope \(m\) of the power-law portion of the structure function
shows no significant correlation with any other parameter
(see Table~\ref{tab:RestStats}),
with a weighted mean value of \(m = 1.01\).
The dispersion in fitted \(m\) values is 1.6 times higher than expected
on the basis of the confidence limits for the individual regions,
implying that there may be a real intrinsic dispersion of \(\pm 0.17\) in the slopes.
However, a \(\chi^2\) test shows that this is only marginally significant
(\(p = 0.11\)), so we cannot rule out that all the slopes are identical.

@@

In Figure~\ref{fig:los-vs-pos} we show the
mean non-thermal line-of-sight velocity dispersion
\(\langle\sigma\los\rangle\)
(obtained from the spectral line profiles)
versus the plane-of-sky dispersion of mean velocities
\(\sigma\pos\)
(obtained from our structure function fits).
The relationship we obtain is
\( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\),
which can be compared with previous results
using different types of samples.
\citet{2011MNRAS.413..705L} surveyed
a sample of small-to-intermediate size \hii{} regions in M33,
finding
\(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
for their sub-sample with higher resolution observations
(21 sources).
This is shown as the dashed line in Figure~\ref{fig:los-vs-pos},
which can be seen to be almost identical to our own result. 
Both fits are consistent with a slope of unity and an offset of
\(\SI{8}{km.s^{-1}}\).
\citet{arthur2016turbulence} calculate the relationship
between \(\langle\sigma\los\rangle\) and \(\sigma\pos\) for different optical emission lines
([\ion{S}{2}], [\ion{N}{2}], \ha, [\ion{O}{3}])
in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
which is shown by the dotted line in Figure~\ref{fig:los-vs-pos}.
Although this line is a fair representation of the low-\(\sigma\)
points in our sample, it fails badly for highest dispersion source,
30~Doradus.

@@

\newcommand\vexp{\ensuremath{v_{\text{exp}}}}
An alternative interpretation,
as discussed in \citet{2011MNRAS.413..705L},
is that \(\sigma\los\) includes a contribution due to
ordered large-scale velocity gradients
(for instance, radial expansion)
in addition to the turbulence,
whereas \(\sigma\pos\) includes only the turbulent motions. 
% Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
Assuming a constant value \vexp{} for the ordered contribution
and that projection smoothing is negligible,
one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
which is shown by the dot-dashed line in Figure~\ref{fig:los-vs-pos}
for the case \(\vexp \approx \SI{8}{km.s^{-1}}\).
It can seen that such a relationship reproduces the 
observationally derived values almost as well as the linear fit.
On the other hand, we can rule out the possibility that
\vexp{} might increase in proportion to the turbulent velocity dispersion
since that would predict that \(\sigma\los \propto \sigma\pos\),
which is inconsistent with the observations as discussed above.

@@

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc2}
  \end{tabular}
  \caption{Effects of finite box size on the structure function.
    (a)~Construction of simulated turbulent velocity fields of different sizes
    by repeated division of an initial field of size \(512 \times 512\) pixels.
    The \(j\)th level of division yields \(N = 4^j\) fields,
    each of linear size \(L \times L\) where \(L = 2^{9 - j}\).
    The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
    (b)~Resultant structure functions.
    Colored lines show the average \(B(r)\) over all sub-images,
    while the shaded areas show the standard deviation of \(B(r)\).
  }
  \label{fig:finite-box}
\end{figure}

@@

Figure~\ref{fig:strucfunc-fit-Galactic}b shows the structure function of the Extended Orion Nebula, which is ten times larger than the core in linear size,
but observed at a much lower angular resolution
(see Figures~\ref{fig:hii-regions} and~\ref{fig:velocity-maps}).
The data for this region are the lowest quality of all the regions in
our sample, and there are too many degeneracies between the parameters
to achieve a credible fit using the full model.
We therefore fix the power slope to \(m = 1\),
which implies that noise makes a significant contribution at all scales
in order to reproduce the observed flat structure function.
In turn, this implies that the true \(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
which is lower than the \SI{7}{km^2.s^{-2}}
that would be naively derived from the observations
(compare green and orange lines in Figure~\ref{fig:strucfunc-fit-Galactic}b).

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
Their results just consider one Gaussian component. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin of error of our own results.

@@

\subsubsection{Comparison with previous studies}
\label{sec:comparison-lagoon}
The structure function of the Lagoon Nebula was previously
studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
finding an approximate power law behavior (\(m = 0.46\))
on scales of \num{0.01} to \SI{0.2}{pc}.
No flattening of the structure function at the largest scales
was seen,
but that is to be expected due to the finite box effect
(see Appendix~\ref{sec:finite-box-effects})
given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
This may be due in part to the fact that \citet{Chakraborty:1999a}
observed a small and atypical part of the nebula known as the
Hourglass region, which includes a cluster of very young stars
\citep{Arias:2006e}. 
In the case of the Orion Nebula we found that the velocity dispersion
of the central region was larger than that of the extended nebula
and this could be an example of a similar phenomenon,
albeit to a more extreme degree.

>>>>

%methods for our analysis
We look for correlations and scaling relations 
between the physical parameters of the \hii{} regions
and the parameters of the fluctuating velocity fields
that we derived in section~\ref{sec:results}.
To accomplish this we implement a hierarchical Bayesian model for linear regression using the \texttt{linmix} Python library, which is based on the procedure of \cite{2007ApJ...665.1489K}.
We fit relations of the form
\(Y = a X + b\)
where \(X = \log_{10} x\) and \(Y = \log_{10} y\)
with \(x, y \in \{d, D_{\hii}, L(\ha), \sigma\pos, r_0, m\}\)
(taken from the physical properties in Table~\ref{tab:regions-properties}
and the derived turbulent parameters of Table~\ref{tab:Res}).
Thus the fitted relation between the original variables
is of the power-law form: \(y = 10^b\, x^a\).
Note that, unlike with an Ordinary Least Squares method,
the \citeauthor{2007ApJ...665.1489K} method
uses an errors-in-variables model that allows for
measurement uncertainty in both \(X\) and \(Y\).
Since the main focus of this paper is the turbulent velocity field,
we restrict consideration to correlations that include
one of the three structure function parameters,
\(\sigma\pos\), \(r_0\), or \(m\), as the  \(y\) variable. 
In addition, we fit a strictly linear relationship between
the plane-of-sky and line-of-sight velocity dispersions:
\(X = \sigma\pos\), \(Y = \sigma\los\).
The reason for not taking the logarithm in this instance is
both to facilitate comparison with previous studies
and to allow for a zero-point offset in the relation.

@@

\subsubsection{The constancy of the power law slope}
\label{sec:constancy-power-law}
The slope \(m\) of the power-law portion of the structure function
shows no significant correlation with any other parameter
(see Table~\ref{tab:RestStats}),
with a weighted mean value of \(m = 1.03\).
The dispersion in fitted \(m\) values is 1.6 times higher than expected
on the basis of the confidence limits for the individual regions,
implying that there may be a real intrinsic dispersion of \(\pm 0.17\) in the slopes.
However, a \(\chi^2\) test shows that this is only marginally significant
(\(p = 0.11\)), so we cannot rule out that all the slopes are identical.

@@

In Figure~\ref{fig:los-vs-pos} we show the
mean non-thermal line-of-sight velocity dispersion
\(\langle\sigma\los\rangle\)
(obtained from the spectral line profiles)
versus the plane-of-sky dispersion of mean velocities
\(\sigma\pos\)
(obtained from our structure function fits).
The relationship we obtain is
\( \langle \sigma\los \rangle = (1.04 \pm 0.44) \sigma\pos + (7.3 \pm 2.9)\),
which can be compared with previous results
using different types of samples.
\citet{2011MNRAS.413..705L} surveyed
a sample of small-to-intermediate size \hii{} regions in M33,
finding
\(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
for their sub-sample with higher resolution observations
(21 sources).
This is shown as the dashed line in Figure~\ref{fig:los-vs-pos},
which can be seen to be almost identical to our own result. 
Both fits are consistent with a slope of unity and an offset of
\(\SI{8}{km.s^{-1}}\).
\citet{arthur2016turbulence} calculate the relationship
between \(\langle\sigma\los\rangle\) and \(\sigma\pos\) for different optical emission lines
([\ion{S}{2}], [\ion{N}{2}], \ha, [\ion{O}{3}])
in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
which is shown by the dotted line in Figure~\ref{fig:los-vs-pos}.
Although this line is a fair representation of the low-\(\sigma\)
points in our sample, it fails badly for highest dispersion source,
30~Doradus.

@@

\newcommand\vexp{\ensuremath{v_{\text{exp}}}}
An alternative interpretation,
as discussed in \citet{2011MNRAS.413..705L},
is that \(\sigma\los\) includes a contribution due to
ordered large-scale velocity gradients
(for instance, radial expansion)
in addition to the turbulence,
whereas \(\sigma\pos\) includes only the turbulent motions. 
% Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
Assuming a constant value \vexp{} for the ordered contribution
and that projection smoothing is negligible,
one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
which is shown by the blue shaded-area in Figure~\ref{fig:los-vs-pos}
with an upper limit of \SI{12}{km.s^{-1}} and lower limit of \SI{8}{km.s^{-1}} for \(\vexp\).
It can be seen that such a relationship reproduces the 
observationally derived values almost as well as the linear fit.
On the other hand, we can rule out the possibility that
\vexp{} might increase in proportion to the turbulent velocity dispersion
since that would predict that \(\sigma\los \propto \sigma\pos\),
which is inconsistent with the observations as discussed above.

@@

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
  \end{tabular}
  \caption{Effects of finite box size on the structure function.
    (a)~Construction of simulated turbulent velocity fields of different sizes
    by repeated division of an initial field of size \(512 \times 512\) pixels.
    The \(j\)th level of division yields \(N = 4^j\) fields,
    each of linear size \(L \times L\) where \(L = 2^{9 - j}\).
    The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
    (b)~Resultant structure functions.
    Colored lines show the average \(B(r)\) over all sub-images,
    while the shaded areas show the standard deviation of \(B(r)\).
  }
  \label{fig:finite-box}
\end{figure}

@@

Figure~\ref{fig:strucfunc-fit-Galactic}b shows the structure function of the Extended Orion Nebula, which is ten times larger than the core in linear size,
but observed at a much lower angular resolution
(see Figures~\ref{fig:hii-regions} and~\ref{fig:velocity-maps}).
The data for this region are the lowest quality of all the regions in
our sample, and there are too many degeneracies between the parameters
to achieve a credible fit using the full model.
We therefore fix the power slope to \(m = 1\),
which implies that noise makes a significant contribution at all scales
in order to reproduce the observed flat structure function.
In turn, this implies that the true \(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
which is lower than the \SI{7}{km^2.s^{-2}}
that would be naively derived from the observations
(compare green and orange lines in Figure~\ref{fig:strucfunc-fit-Galactic}b).
The derived correlation length is \SI{0.5}{pc} which is above the \SI{0.3}{pc} required to determine the true correlation length but below the \SI{0.9}{pc} which guarantees that the fit can reliable determine \(r_0\). 
The structure function at large scales resembles the tapered behavior of inhomogeneous fluctuations just like the core.

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
Their results just consider one Gaussian component. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin of error of our own results.

@@

\subsubsection{Comparison with previous studies}
\label{sec:comparison-lagoon}
The structure function of the Lagoon Nebula was previously
studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
finding an approximate power law behavior (\(m = 0.46\))
on scales of \num{0.01} to \SI{0.2}{pc}.
No flattening of the structure function at the largest scales was seen, but that is to be expected due to the finite box effect (see Appendix~\ref{sec:finite-box-effects}).
Given that we determine the correlation length to be \(r_0 \approx \SI{1}{pc}\) for this nebula,
which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
This may be due in part to the fact that \citet{Chakraborty:1999a}
observed a small and atypical part of the nebula known as the
Hourglass region, which includes a cluster of very young stars
\citep{Arias:2006e}. 
In the case of the Orion Nebula we found that the velocity dispersion
of the central region was larger than that of the extended nebula
and this could be an example of a similar phenomenon,
albeit to a more extreme degree.
